### 2015-09-12 paper/main.tex
Fix display of superlong equation

\subsection{Preferential Trade Liberalization}
The model results and estimation equations presented so far all referred to a unilateral trade liberalization in a simplified two-country setup\footnote{Note that a bilateral trade liberalization -- changing $\tau$ and $\tau^*$ by the same amount -- would not lead to the discussed short- and long run changes in cost cutoffs for two countries, but instead to a decline in the cost cutoffs in both countries both in the short and the long run.}. While making the exposition clearer and helping to elicit the effects at work in the model, this setup is clearly not an accurate description of the reality of trade relationships in modern industrialized economies. Taking the United States as an example, while the two other countries in our data set, Canada and Mexico, are its largest trading partners, they only account for 16.6 and 13.5\% of all US trade by value, respectively\footnote{See \href{Top U.S. Trade Partners, U.S. International Trade Administration}{http://www.trade.gov/mas/ian/build/groups/public/@tg_ian/documents/webcontent/tg_ian_003364.pdf}}. Even the largest 30 US trading partners only account for about 86\% of US trade, highlighting the fragmented nature of international trade. While the Melitz-Ottaviano model can be extended to an arbitrary number of countries, it is clearly not feasible to assemble a data set on all trade partners of the NAFTA countries. We do however want to recognize the multi-country structure of NAFTA by taking into account third country effects of trade barriers. Here, NAFTA can be interpreted as a preferential liberalization of Mexico \textit{vis-a-vis} the US and Canada, as Mexico had the highest tariff barriers to start off with. In the three country case, we expect the country with the lowest sum of bilateral trade barriers to have the lowest cost cutoff, as it becomes the best export hub. To account for this, we amend equations \ref{eq:gw-estimation-prices}, \ref{eq:gw-estimation-markup} and \ref{eq:gw-estimation-productivity by including the relevant third country tariffs. The estimation equation for the effects of trade barriers on prices then becomes:

\begin{align}
\begin{split}\label{eq:gw-estimation-prices}
\Delta \ln \left( \frac{\bar{p}_{it}}{\bar{p}_{it}^*} \right) = &\beta_0 + \beta_1 \Delta \ln \tau_{it} + \beta_2 \Delta \ln \tau_{it}^* + \beta_3 \Delta \ln \tau_{it}^{ht} + \beta_4 \Delta \ln \tau_{it}^{th} + \beta_5 \Delta \ln \tau_{it}^{ft} + \beta_6 \Delta \ln \tau_{it}^{th}+  \beta_7 \Delta \ln D_{it} + \beta_8 \Delta \ln D_{it}^* + \beta_9 \Delta \ln D_{it}^t \\ &+ \gamma \left[ \ln \left( \frac{\bar{p}_{it-1}}{\bar{p}_{it-1}^*} \right) + \delta_0 + \delta_1 \ln L_{t-1} + \delta_2\ln L_{t-1}^* + \delta_3 \ln L_{t-1}^t+ \delta_4 \ln  \tau_{i,t-1} + \delta_5 \ln  \tau_{i,t-1}^*  + 
\delta_6 \Delta \ln \tau_{it}^{ht} + \delta_7 \Delta \ln \tau_{it}^{th} + \delta_8 \Delta \ln \tau_{it}^{ft} + \delta_9 \Delta \ln \tau_{it}^{th}\right] + \varepsilon_{ijt} 
\end{split}\end{align}
where now $h$ is the domestic economy, $f$ is the foreign economy, and, with a slight abuse of notation, a $t$ superscript denotes the third country for each country pair (e.g. when estimating the Canada-US relationship, $\tau^{th}$ are Mexican tariffs on Canadian goods, while $\tau^{ht}$ are Canadian tariffs on Mexican goods).

>>>>

\subsection{Preferential Trade Liberalization}
The model results and estimation equations presented so far all referred to a 
unilateral trade liberalization in a simplified two-country setup\footnote{Note
 that a bilateral trade liberalization -- changing $\tau$ and
 $\tau^*$ by the same amount -- would not lead to the discussed short- and long 
run changes in cost cutoffs for two countries, but instead to a decline in the cost cutoffs in both countries both in the short and the 
long run.}. While making the exposition clearer and helping to elicit the effects at work in the model, this setup is clearly not an accurate description of the reality of trade relationships in modern industrialized economies. Taking the United States as an example, while the two other countries in our data set, Canada and Mexico, are its largest 
trading partners, they only account for 16.6 and 13.5\% of all US trade by value, 
respectively\footnote{See \href{Top U.S. Trade Partners, U.S. International Trade Administration}{http://goo.gl/2C0saQ}}. 
Even the largest 30 US trading partners only account for about 86\% of US trade, highlighting the fragmented nature of international trade. While the Melitz-Ottaviano model can be extended to an arbitrary number of countries, it is clearly not feasible to assemble a data set on all trade partners of the NAFTA countries. We do however want to recognize the multi-country structure of NAFTA by taking into account third country effects of trade barriers. Here, NAFTA can be interpreted as a preferential liberalization of Mexico \textit{vis-a-vis} the US and Canada, as Mexico had the highest tariff barriers to start off with. In the three country case, we expect the country with the lowest sum of bilateral trade barriers to have the lowest cost cutoff, as it becomes the best export hub. To account for this, we amend equations \ref{eq:gw-estimation-prices}, \ref{eq:gw-estimation-markup} and \ref{eq:gw-estimation-productivity} by including the relevant third country tariffs. The estimation equation for the effects of trade barriers on prices then becomes:

\begin{align}
\begin{split}\label{eq:gw-estimation-prices-third-country}
\Delta \ln \left( \frac{\bar{p}_{it}}{\bar{p}_{it}^*} \right) = 
&\beta_0 + \beta_1 \Delta \ln \tau_{it} + \beta_2 \Delta \ln \tau_{it}^* + \beta_3 \Delta \ln \tau_{it}^{ht} 
+ \beta_4 \Delta \ln \tau_{it}^{th} + \beta_5 \Delta \ln \tau_{it}^{ft} + \beta_6 \Delta \ln \tau_{it}^{th} \\ 
&+ \beta_7 \Delta \ln D_{it} + \beta_8 \Delta \ln D_{it}^* + \beta_9 \Delta \ln D_{it}^t \\ 
&+ \gamma \left[ \ln \left( \frac{\bar{p}_{it-1}}{\bar{p}_{it-1}^*} \right) + \delta_0 + \delta_1 \ln L_{t-1} + \delta_2\ln L_{t-1}^* 
 + \delta_3 \ln L_{t-1}^t+ \delta_4 \ln \tau_{i,t-1} \right. \\ 
&+ \left. \delta_5 \ln  \tau_{i,t-1}^*  + \delta_6 \Delta \ln \tau_{it}^{ht} + \delta_7 \Delta \ln \tau_{it}^{th} 
 + \delta_8 \Delta \ln \tau_{it}^{ft} + \delta_9 \Delta \ln \tau_{it}^{th} \bigg] \right. + \varepsilon_{ijt} 
\end{split}\end{align}
where now $h$ is the domestic economy, $f$ is the foreign economy, and, with a slight abuse of notation, a $t$ superscript denotes the third country for each country pair (e.g. when estimating the Canada-US relationship, $\tau^{th}$ are Mexican tariffs on Canadian goods, while $\tau^{ht}$ are Canadian tariffs on Mexican goods). Both the equations for markups and productivity will be amended accordingly.
